### 2020-06-29 main.tex
:pencil: Abstract

\begin{section}{Introduction}
	With the great advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks. Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the radio-frequency (RF) band. It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner. The decreasing trend in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.

	The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the rate-energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels. Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between energy harvesting (EH) and Information Decoding (ID) modes and Power Splitting (PS) that splits the received signal into individual components. On top of this, \cite{Zhang2013} characterized the R-E region for a multiple-input multiple-output (MIMO) broadcast system under TS and PS setup. Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}. Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems. However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level. The authors also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm. From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency. \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current under rate constraints. Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}. The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is optimized to enlarge the R-E region. In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications. By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adjusted conventional modulation schemes to ensure WPT is only activated at the points with large offset. Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the information symbols are symmetrically distributed around the origin. It confirmed that the superposed waveform is feasible to enlarge R-E region when considering rectifier nonlinearity. SWIPT was also explored in the network design. \cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user. In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted Sum-Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).

	Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal. It also contributes to a quadratic increase of received signal power with the number of reflectors, which can be interpreted as a Maximum Ratio Combining (MRC) receiver overlapped to a Maximum Ratio Transmission (MRT) transmitter.

	Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate path loss and multi-path fading. At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to solve indoor signal blockage problem. Motivated by this, \cite{Wu2018,Wu2019} introduced an IRS-assisted MISO system and proposed a beamforming algorithm that jointly optimizes the precoder at the Access Point (AP) and the phase shifts at the IRS to maximize Signal-to-Noise Ratio (SNR). The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}. In \cite{Nadeem2019}, channel estimation for Time Division Duplex (TDD) systems was performed through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially evaluates the cascaded channel of each IRS element with the others switched off. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency Division Multiplexing (OFDM) systems. A practical transmission protocol was proposed in \cite{Yang2019}, where the authors exploited spatial correlation to reduce estimation overhead and optimization complexity by assuming adjacent elements share a common reflection coefficient. On top of this, group-based OFDM channel estimation was investigated in \cite{Zheng2019}. \cite{Yang2020} proposed a dynamic passive beamforming strategy that adapts IRS over time slots to create time-varying channels within coherence time and exploits the diversity by updating resource allocation and IRS configuration alternatively. Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.

	The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. Based on linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints. The fairness issue was then considered in \cite{Tang2019}, which assumed perfect energy interference cancellation and maximized the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques. \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power since the rank-deficient channels are highly correlated such that a single energy stream can satisfy the energy constraints of all ERs. In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms. However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
\end{section}

\begin{section}{System Model}
	Consider an IRS-aided multiuser SISO SWIPT system where the IRS not only assists the primal transmission but also retrieves Channel State Information (CSI) and harvests energy for its own operation. The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$). Suppose each subband is allocated to one user per time slot. It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}. Due to the passive characteristics of IRS, we consider a Time-Division Duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity. Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system. A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame. The signals reflected by IRS for two and more times are assumed negligible and thus not considered. Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}. Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with the same reflection coefficients for all subbands. Since a deterministic multisine waveform can boost the energy transfer efficiency \cite{Clerckx2016a} and creates no interference to the information signal \cite{Clerckx2018b}, we use a superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, to maximize the rate-energy tradeoff. Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester. In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\lambda)$ and $\lambda$ respectively. Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\lambda=1$ and wireless information transfer (WIT) with $\lambda=0$. The adjustment of $\lambda$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots. In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$ such that the PS ratio is coupled with waveform design. Perfect synchronization is assumed among the three parties in both scenarios.

>>>>

\begin{abstract}
	Simultaneous Wireless Information and Power Transfer (SWIPT) is limited by the low power level of the receive Radio-Frequency (RF) signal. To tackle this problem, we introduce Intelligent Reflecting Surface (IRS) that brings a high passive beamforming gain by adjusting reflecting elements, which compensates the propagation loss and boosts the energy efficiency with low power consumption. This paper investigates an IRS-aided multiuser Orthogonal Frequency Division Multiplexing (OFDM) SWIPT system based on practical nonlinear harvester model, where the single-antenna Access Point (AP) transmits information and energy simultaneously to multiple single-antenna users under the assist of IRS. We aim to maximize the weighted sum Rate-Energy (R-E) region via jointly optimizing the transmit waveform at the AP, the phase shifts at the IRS, and the power splitting ratio at all users. The problem is transformed to a current maximization problem subject to rate constraint, and we propose an low-complexity alternating algorithm to obtain suboptimal solutions iteratively. Simulation results demonstrated significant R-E region enlargement over benchmark schemes when IRS is properly configured.
\end{abstract}

\begin{section}{Introduction}
	\begin{subsection}{Simultaneous Wireless Information and Power Transfer}
		With the great advance in communication performance (throughput, latency, outage), the main challenge of wireless network has come to energy supply. Most existing mobile devices are powered by batteries that require frequent charging or replacement, which leads to high maintenance cost and thus restricts the scale of networks. Although solar energy and inductive coupling has become popular alternatives, the former depends on the environment while the latter has a very short operation range. Simultaneous Wireless Information and Power Transfer (SWIPT) is a promising solution to connect and power mobile devices via electromagnetic (EM) waves in the Radio-Frequency (RF) band. It provides low power (in \si{\uW} level) but broad coverage (up to hundreds of meters) \cite{Ng2018} in a sustainable and controllable manner. The decreasing trend in electronic power consumption also boosts the paradigm shift from dedicated power source to Wireless Power Transfer (WPT) and SWIPT.

		The concept of SWIPT were first cast in \cite{Varshney2008}, where the authors investigated the Rate-Energy (R-E) tradeoff for a flat Gaussian channel and some discrete channels. Two practical receiver structures were then proposed in \cite{Zhou2013}, namely Time Switching (TS) that switches between energy harvesting (EH) and Information Decoding (ID) modes, and Power Splitting (PS) that splits the received signal into individual components. On top of this, \cite{Zhang2013} characterized the R-E region for a Multiple-Input Multiple-Output (MIMO) broadcast system under TS and PS setup. Information and power beamforming was then considered in multi-user multi-input single-output (MISO) systems to maximize the Weighted Sum-Power (WSP) subjective to Signal-to-Interference-plus-Noise Ratio (SINR) constraints \cite{Xu2014}. Motivated by this, \cite{Krikidis2014} investigated fundamental transceiver modules, information and power scheduling, and interference management for SWIPT systems. However, \cite{Boshkovska2015} pointed out that the Radio Frequency (RF)-to-Direct Current (DC) conversion efficiency depends on the harvester input power level, which also suggested a parametric harvester model based on curve fitting and proposed an iterative resource allocation algorithm. From another perspective, \cite{Trotter2009,Boaventura2011} demonstrated that multisine waveform is more suitable for WPT as it outperforms single tone in both operation range and RF-to-DC efficiency. \cite{Clerckx2016a} derived a tractable nonlinear harvester model based on the Taylor expansion of diode I-V characteristics and proposed an adaptive waveform optimization algorithm to maximize the output DC current under rate constraints. Simulation and experiments demonstrated the benefit of modelling rectifier nonlinearity in system design \cite{Kim2019,Kim2019a}. The work was extended to SWIPT in \cite{Clerckx2018} where a superposition of modulated information waveform and multisine power waveform is optimized to enlarge the R-E region. In contrast, \cite{Park2018} suggested an adaptive dual-mode SWIPT, which alternates between single-tone transmission that exploits conventional modulation for high-rate applications and multisine transmission that encodes the information in the Peak-to-Average Ratio (PAPR) for power-demanding applications. By assuming On-Off-Keying (OOK) where bit 1 carries energy, \cite{Hu2019} compared unary and Run-Length-Limited (RLL) code in terms of rate vs battery overflow/underflow probability, and adapted conventional modulation schemes to ensure WPT is only activated at the points with large offset. Also, a learning approach \cite{Varasteh2019c} demonstrated that the offset of the power symbol is positively correlated to the harvester energy constraint, while the information symbols are symmetrically distributed around the origin. It confirmed that the superposed waveform is feasible to enlarge R-E region when considering rectifier nonlinearity. SWIPT was also explored in the network design. \cite{Liu2016} proposed a cooperative SWIPT Non-Orthogonal Multiple Access (NOMA) protocol with three user selection schemes such that the strong user assists the EH of the weak user. In \cite{Mao2019}, SWIPT based on Rate Splitting (RS) was formulated as a Weighted Sum-Rate (WSR) maximization problem subject to total harvested energy constraint for separated Information Receivers (IRs) and Energy Receivers (ERs).
	\end{subsection}

	\begin{subsection}{Intelligent Reflecting Surface}
		Intelligent Reflecting Surface (IRS) adapts the wireless environment to increase spectrum and energy efficiency. In practice, an IRS consists of multiple individual reflecting elements that adjust the amplitude and phase of the incident signal through passive beamforming. Different from relay and backscatter communication, IRS assists the primary transmission without any active components, leading to low power consumption and no thermal noise added to the reflected signal. Compared with the linear increase in Amplify-and-Forward (AF) relay, the received power scales quadratically with the number of reflectors \cite{Wu2019}, which can be interpreted as a Maximum Ratio Combining (MRC) superposed to a Maximum Ratio Transmission (MRT).

		Inspired by the advance in real-time reconfigurable metamaterials \cite{Cui2014}, \cite{Liaskos2018} introduced a programmable metasurface that steers or polarizes the EM wave at specific frequency to mitigate path loss and multi-path fading. At the same time, \cite{Tan2018} constructed an adjustable reflect array that ensures reliable millimeter-wave (mmWave) communication based on a beam-searching algorithm to reduce indoor signal blockage. Motivated by this, \cite{Wu2018,Wu2019} introduced an IRS-assisted MISO system and proposed a beamforming algorithm that jointly optimizes the precoder at the Access Point (AP) and the phase shifts at the IRS to maximize Signal-to-Noise Ratio (SNR). The active and passive beamforming problem was extended to the discrete phase shift case \cite{Wu2019a} and the multiuser case \cite{Guo2019a}. In \cite{Nadeem2019}, channel estimation for Time Division Duplex (TDD) systems was carried through a two-stage Minimum Mean Squared Error (MMSE)-based protocol that sequentially estimates the cascaded channel of each IRS element with the others switched off. Starting from the impedance equation, \cite{Abeywickrama2019} investigated the influence of phase shift on the reflection amplitude and proposed a parametric IRS model via curve fitting. Recent research also explored the opportunity of integrating IRS with Orthogonal Frequency Division Multiplexing (OFDM) systems. \cite{Yang2019} exploited spatial correlation to reduce estimation overhead and design complexity by assuming adjacent elements share a common reflection coefficient. On top of this, group-based OFDM channel estimation was investigated in \cite{Zheng2019}. By adjusting IRS over time slots, \cite{Yang2020} introduced artificial diversity within coherence time and investigated resource allocation and IRS configuration per Resource Block (RB). Real-time high-definition video transmission was performed over a prototype constructed with Positive Intrinsic-Negative (PIN) diodes, which demonstrated the feasibility and benefit of IRS at GHz and mmWave frequency \cite{Dai2020}.
	\end{subsection}

	\begin{subsection}{IRS-aided SWIPT}
		The effective channel enhancement and low power consumption of IRS are expected to bring more opportunities to SWIPT. Assuming linear harvester model with energy interference, \cite{Wu2019b} proved that at most one energy beam is required to maximize the WSP subject to SINR constraints. The fairness issue was then considered in \cite{Tang2019}, which maximize the minimum output power based on Alternating Optimization (AO) and Semi-Definite Relaxation (SDR) techniques based on perfect energy interference cancellation. \cite{Wu2019c} proposed a novel penalty-based algorithm, whose inner layer employs Block Coordinate Descent (BCD) method to update precoders, phase shifts and auxiliary variables while the outer layer updates the penalty coefficients. It demonstrated that Line-of-Sight (LoS) links can boost the harvested power since the rank-deficient channels are highly correlated such that a single energy stream can satisfy the energy constraints of all ERs. In \cite{Pan2019a}, the WSR maximization of MIMO SWIPT was first transformed to Weighted Minimum Mean Square Error (WMMSE) problem then solved by BCD with low-complexity iterative algorithms. However, most existing IRS-SWIPT papers focus on narrow-band transmission over linear harvester model.
	\end{subsection}

	\begin{subsection}{Research Proposal}
		In this paper, we consider an IRS-aided multiuser Single-Input Single-Output (SISO) OFDM SWIPT system based on practical nonlinear harvester model.
	\end{subsection}
\end{section}

\begin{section}{System Model}
	Consider an IRS-aided multiuser SISO OFDM SWIPT system where the IRS assists the information and energy transmission of all users. The single-antenna transmitter delivers information and power simultaneously, through the $L$-reflector IRS, to $K$ single-antenna users over $N$ orthogonal subbands. Assume a total bandwidth $B$ and evenly-spaced carriers around center frequency $f_0$. Denote the frequency of the $n$-th subband as $f_n$ ($n=1,\dots,N$). Suppose each subband is allocated to one user per time slot. It is assumed that the IRS performs channel estimation in the first subframe and supports information and power transfer in the second subframe \cite{Zheng2019}. Due to the passive characteristics of IRS, we consider a Time-Division Duplexing (TDD) protocol where the CSI can be obtained by exploiting channel reciprocity. Perfect CSI is assumed at the AP and IRS to investigate the analytical upper-bound of the proposed system. A quasi-static frequency-selective model is used for both the AP-user and AP-IRS-user links where the channels are assumed unchanged within each transmission frame. The signals reflected by IRS for two and more times are assumed negligible and thus not considered. Note that although Frequency Selective Surface (FSS) has received much attention for wideband communications, active FSS requires RF-chains thus becomes prohibitive in IRS \cite{Kim2006,Xu2014}. Since passive FSS is not reconfigurable with fixed physical characteristics \cite{Anwar2018}, we assume a frequency-flat IRS with the same reflection coefficients for all subbands. Since a deterministic multisine waveform can boost the energy transfer efficiency \cite{Clerckx2016a} and creates no interference to the information signal \cite{Clerckx2018b}, we use a superposition of multicarrier modulated and unmodulated waveforms, both transmitted on the same frequency bands, to maximize the rate-energy tradeoff. Two practical receiver architectures proposed in \cite{Zhang2013}, namely Time Switching (TS) and Power Splitting (PS), are investigated for the co-located information decoder and energy harvester. In the TS strategy, each transmission subframe is further divided into orthogonal data and energy slots, with duration ratio $(1-\lambda)$ and $\lambda$ respectively. Hence, the achievable rate-energy region can be obtained through a time sharing between wireless power transfer (WPT) with $\lambda=1$ and wireless information transfer (WIT) with $\lambda=0$. The adjustment of $\lambda$ has no impact on the transmit waveform and IRS elements design as they are optimized individually in data and energy slots. In comparison, the PS scheme splits the received signal into data and energy streams with power ratio $(1-\rho)$ and $\rho$ such that the PS ratio is coupled with waveform design. Perfect synchronization is assumed among the three parties in both scenarios.
